---
title: "Lab 3"
author: "Luz Rosado"
date: '2022-03-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(spData)
library(rnaturalearth)
library(sp)
```

# Excercise 1
1. ESRI Shape file - ESRI Shapefile is a vector fomrat that requires at least three files to 
work properly. The .shp file stores the geometries, the .prj file stores the projection 
inormation for the geometries, and the .shx stores the shape definitions. 
2. GeoTIFF - Contains raster image and raster metadata. Probably one of the most popular
ways to store raster data.
3. ESRI FileGDB - Database file that stores the spatial and non-spatial data of a raster
or a vector. File is created in arcgis.

# Excercise 2
read_sf() and st_read() are essentially the same and are aliases for one another.
read_sf() however does not print information about the data source when called,
and sf_read() returns and tibble rather than a data frame. 

# Excercise 3

```{r}
cycle_hire <- st_read(system.file("misc/cycle_hire_xy.csv", package="spData"))
```
There is no geometry in the loaded file, so the loaded object is a data frame. 

# Excercise 4

```{r }
germany_borders = ne_download(scale = 110, type = "countries", category = c("physical"), returnclass = c("sp", "sf"))

write_sf(obj = world, dsn = "world.gpkg")
```